---
title: "Exposure_T2_HT2_Euromix"
author: "Trine Husøy"
date: "2025-09-17"
output: html_document
---

## R Markdown

Define knitr chunk options

For more info in Markdown and knitr chunk options see [rmarkdown-cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html)
```{r setup, include=TRUE}
knitr::opts_chunk$set(
  comment = "#>", echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, fig.width = 6)
```

# Activate packages
```{r}
#install.packages("xfun")

library(writexl)
library(plyr)
library(openxlsx)
library(tidyverse)
library(fitdistrplus)
library(ggridges)
library(flextable)

```

# Get work directory and organise results

```{r}

HOME <- "C:/Users/TRHU/Documents/R/T2_HT_2"
setwd(HOME)

```

Create a folder with current date in the Result folder
```{r}

newday <- file.path('C:/Users/TRHU/Documents/R/T2_HT_2/Results', Sys.Date())
dir.create(newday)

```

# Read in data

To knit the file to word or html we need to chande the code below from "../Data/......." to "./Data/........", putting in an extra dot before the /Data.
```{r}
ID <- read_csv2("../Data/Selected_ID.csv") # The IDs in EuroMix selected for the T2/HT2 project
Consumption <- read_csv2("../Data/Consumption_dummy.csv", locale = locale(encoding = "UTF-8"))
Occurance_NO_2015 <- read_delim("../Data/Occurance_NO_2015.csv") # Occurrence from 2015 to 2023
Occurance_NO_2008to10 <- read_delim("../Data/PAD_2023_049_T2_HT2_NO only.csv")

```


## To be able to read æ,ø and å run in the console the code below.

 Then it will be possible to search for words with Scandinavian letters
```{r}
##### IMPORTANT
Sys.setlocale(locale='no_NB.utf8')

```


# Functions

This is a function whith make R recognise scandinavian letters æ, ø and å. Makes it possible to search in the norwegian food categories
```{r}
# Create a function to convert all columns to UTF-8 encoding,
# dropping any characters that can't be converted.
f_df_convert_utf8 <- function(df_data){

  # Convert all character columns to UTF-8
  # Source: https://stackoverflow.com/questions/54633054/dbidbwritetable-invalid-multibyte-string
  df_data[,sapply(df_data,is.character)] <- sapply(
    df_data[,sapply(df_data,is.character)],
    iconv,"WINDOWS-1252","UTF-8",sub = "")
  
  return(df_data)
}

```

Calculate the location (Loc) and scale (shape) parameters for a log normal distribution
```{r}

f_lognorm_Loc <- function(x){
  log(
    x$mean^2/sqrt(x$sd^2+x$mean^2)
  )
  
}


f_lognorm_shape <- function(x){
  sqrt(
    log(
      1 + x$sd^2/x$mean^2
    )
  )
}
```

The function gives N, mean and sd for a numeric vector
```{r}
f_summ <-function(x){
  x %>%
  dplyr::summarise(
    N = n(),
    mean = mean(value, na.rm=TRUE),
    sd=sd(value, na.rm=TRUE)
  )
}  
```

This function sample the concentrations from a log normal distribution of T2 or HT2 toxin measured in grain for each publication equal to the number of analyses that has been done. The sampled concentrations for each grain is added and summary data is calculated as a basis for a overall log normal distribution of concentrations of T2 and HT2 toxin in the grain. The overall conc distribution is used for "baking" of bread, fine bakery and crisp bread.
```{r}


#-----------------------------------------------------------------------------------
# never introduce a local variable with the same name as an input variable
# just define x as list with length equal to nrow(y)
# combine all elements of list with unlist(.)
# carefully check your indexing; R is very sloppy in this respect
#-----------------------------------------------------------------------------------


f_conc_grain <- function(y){
   x <- vector("list", length = nrow(y))
  for(i in 1:nrow(y)){
    set.seed(123)
    x[[i]] <- rlnorm(n=y$sample_size[i], y$mu[i], y$var[i])
  }
  x <- unlist(x)
  x <- list(name = 1:length(x), value = x)
  x <- as_tibble(x)
  x <- f_summ(x) # make summary data
  x$Loc <- f_lognorm_Loc(x) # Location parameter for the log normal distribution
  x$shape <- f_lognorm_shape(x) # Shape parameter for the log normal distribution
  return(x)
}

```


## Functions for calculating T2/HT2 concentrations in bakery products, oat bread and cereals
Taking the receipts from the Norwegian "matvaretabell" or from the Norwegian dietary calculation system "KBS". Since the EuroMix study is registered in KBS and the consumption of different food are calculated in KBS, I have selected the receipts form KBS.

Bread with 50-70% grain contents for 100g bread:
37.3 g ground wheat 
37.3 g ground whole wheat
37.3 g water
1.3 g yeast
1 g salt

Oat bread:
38.1 g "ground" wheat 
38.1 g oat grain
38.1 g water
1.1 g yeast
1.5 g salt


```{r}
f_MC_bakery <- function(y){ # T2/HT2 (ng) concentration in g bakery
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.746 * rlnorm(n=1,y$Loc[i], y$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

f_MC_oatbread <- function(y, z){ # T2/HT2 (ng) concentration in g oatbread
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.381 * rlnorm(n=1,y$Loc[i], y$shape[i]) + 0.381 * rlnorm(n=1,z$Loc[i], z$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

```

For cereals the declaration of content shows that oat is on the top three ingredients that is listed, which means that oat is a major ingredient in cereals sold in Norway. For the cereal with fruit (AXA), oat were listed before fruit(25%), which means that the content of oat is higher than 25%. I therefore assume that the oat content is 30% in all cereals eaten in Euromix. Since the cereals also contain wheat grain and rye, I assume that 60% of the cereal is wheat and rye

```{r}
f_MC_cereal <- function(y, z){ # T2/HT2 (ng) concentration in g cereal, y is cons in oat, and z is conc in wheat_rye
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.3 * rlnorm(n=1,y$Loc[i], y$shape[i]) + 0.6 * rlnorm(n=1,z$Loc[i], z$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

```

For the oatmilk we have no defined receipt how much oat per ml water is used in commercial products, but from receipt online about 50-200 g out is used to 1000ml water. This results in 800 ml drink. This is in line with what is reported in UK with 10-12 g oat per 100 ml water. I choose to use 100 g per 1000 ml water, which results in 800 ml, which amount to approximately 10% oat. 

```{r}
f_MC_oatmilk <- function(y){ # T2/HT2 (ng) concentration in g oatmilk, y is cons in oat
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.1 * rlnorm(n=1,y$Loc[i], y$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

```

## Function for doing the Monte Carlo simmulation 


```{r}
f_MC_Sim <- function(x,y){
  x$Loc <- y$Loc[match(x$foodcat, y$foodcat)] # Identify the right Loc and shape parameter for the food category
  x$shape <- y$shape[match(x$foodcat, y$foodcat)]
  
  MC <- replicate(1000, x$Amount*
                    rlnorm(n=105,x$Loc, x$shape), simplify = FALSE)
  
  df_MC <- as.data.frame(do.call(cbind, MC))
  x <- cbind(x, df_MC)
  
  return(x)
  }

```


# Cleaning of data

Separate IDs for day 1 and day 2, to be used for selection of IDs of the consumption file
```{r}
ID_day1 <- ID[ID$Day==1,]
ID_day2 <- ID[ID$Day==2,]

```


## Clean consumption data
```{r}

# Use the function f_df_convert_utf8 to be able to read Norwegian letters, æ, ø, and å
Consumption <- f_df_convert_utf8(Consumption)
Consumption <- Consumption %>% dplyr::select(-Food_nr)

Consumption_day1 <- Consumption[Consumption$Day==1,] # Separate consumption for day 1 and day 2
Consumption_day2 <- Consumption[Consumption$Day==2,]

# Select the IDs included in the T2/HT2 project

Consumption_day1 <- Consumption_day1[Consumption_day1$Idkode %in% ID_day1$IDkode,]
Consumption_day2 <- Consumption_day2[Consumption_day2$Idkode %in% ID_day2$IDkode,]

Consumption_T2 <- rbind(Consumption_day1, Consumption_day2)

```

### Select the consumption relevant for exposure to T2/HT2 toxin

This is dependent on the concentration file on T2/HT2 toxin and the food categories represented there. We will select these food categories from the consumption file, and group them into broader consumption groups.

```{r}

cereals <- c("(?i)Havrefras", "(?i)Crusli", "(?i)mysli", "(?i)frokost", "(?i)cornflakes", "(?i)4-korn") 
cereal <- Consumption_T2[str_detect(Consumption_T2$Name, paste(cereals, collapse = "|")),]
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, paste(cereals, collapse = "|")),]
cereal$foodcat <- "cereal"


oat <- c("(?i)havregryn", "(?i)havremel")
oat <- Consumption_T2[str_detect(Consumption_T2$Name, paste(oat, collapse = "|")),]
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, paste(oat, collapse = "|")),]

oatmilk <- oat[str_detect(oat$Name, "(?i)melk"),]
oatmilk$foodcat <- "oatmilk"
Consumption <- rbind(cereal, oatmilk)

oat <- oat[!str_detect(oat$Name, "(?i)melk"),]
oat$foodcat <- "oat"
Consumption <- rbind(Consumption, oat)

oat <- Consumption_T2[str_detect(Consumption_T2$Name, "(?i)havr"),] # Extract food with oat
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, "(?i)havr"),]
oatbread <- oat[str_detect(oat$Name, "(?i)brød"),] # Extract the bread with oat
oatbread$foodcat <- "oatbread"
Consumption <- rbind(Consumption, oatbread)
oat <- oat[!str_detect(oat$Name, "(?i)brød"),]


bakery_fine <- c("(?i)rundst", "(?i)boll", "(?i)tortilla", "(?i)hamburgerbrød", "(?i)polarbrød", "(?i)brød", "(?i)knekkebr", "(?i)rug sammalt", "(?i)hvete")
bakery <- Consumption_T2[str_detect(Consumption_T2$Name, paste(bakery_fine, collapse = "|")),]
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, paste(bakery_fine, collapse = "|")),]
bakery$foodcat <- "bakery"
Consumption <- rbind(Consumption, bakery)

Consumption <- Consumption %>% arrange(Idkode, Meal) # arrange the file after ID and meals
Consumption$Amount <- as.numeric(Consumption$Amount)
```

## Clean Norwegian occurance data

The Norwegian occurence data is received from EFSA, as all the Norwegian contaminant analyses in Norwegian food are reported to EFSA. The unit for the data are microgram/kg, which is the same as ng/g. These data are individual analyses, and are treated as such. It is likely that these analyses are perform on merged samples as this is common practice in Norway, and we will therefore loose some of the variability of the samples which will affect the tail of the distribution. 

Cleaning the Norwegian data from 2008 to 2010
```{r}
Occurance_NO_2008 <- Occurance_NO_2008to10 %>% dplyr::select(c("PARAMTEXT", "ANMATCODE_BASE_ID", "RESVAL", "RESLOD", "RESLOQ")) # Select relevant coloumns

colnames(Occurance_NO_2008) <- c("type", "FoodEx", "value", "RESLOD", "RESLOQ") # Change coloumn names

# Make a new column called raw wih the name of the food/grain in that row
Occurance_NO_2008 <- Occurance_NO_2008 %>%
  mutate(raw = case_when(
    str_detect(str_to_lower(FoodEx), "oat") ~ "oat",
    str_detect(str_to_lower(FoodEx), "wheat") ~ "wheat",
    TRUE ~ NA_character_  # eller "ukjent" hvis du vil ha en verdi
  ))

# Wheat
#--------------

Occurance_NO_2008_wheat_flour <- Occurance_NO_2008 %>% filter(str_detect(FoodEx, "flour"))

# Merge the values from LOD and LOQ into a new coloumn
Occurance_NO_2008_wheat_flour <- Occurance_NO_2008_wheat_flour %>%
  mutate(LOD_Q = if_else(is.na(RESLOD), RESLOQ, RESLOD))

# Replace the NA's with half LOD or LOQ, medium bound

Occurance_NO_2008_wheat_flour <- Occurance_NO_2008_wheat_flour %>%
  mutate(value = case_when(
    is.na(value) & !is.na(LOD_Q) ~ LOD_Q / 2,
    TRUE ~ value
  ))



Occurance_NO_2008_bran <- Occurance_NO_2008 %>% filter(str_detect(FoodEx, "bran")) # bran are wheat grain

# Merge the values from LOD and LOQ
Occurance_NO_2008_bran <- Occurance_NO_2008_bran %>%
  mutate(LOD_Q = if_else(is.na(RESLOD), RESLOQ, RESLOD))

# Replace the NA's with LOD or LOQ, medium bound

Occurance_NO_2008_bran <- Occurance_NO_2008_bran %>%
  mutate(value = case_when(
    is.na(value) & !is.na(LOD_Q) ~ LOD_Q / 2,
    TRUE ~ value
  ))




# Oat
#--------

Occurance_NO_2008_oat <- Occurance_NO_2008 %>% filter(str_detect(FoodEx, "oat"))

# Merge the values from LOD and LOQ
Occurance_NO_2008_oat <- Occurance_NO_2008_oat %>%
  mutate(LOD_Q = if_else(is.na(RESLOD), RESLOQ, RESLOD))

# Replace the NA's with LOD or LOQ, medium bound

Occurance_NO_2008_oat <- Occurance_NO_2008_oat %>%
  mutate(value = case_when(
    is.na(value) & !is.na(LOD_Q) ~ LOD_Q / 2,
    TRUE ~ value
  ))



```
The conclusion from the testing of positive analyses for the 2008-2010 data file above is that wheat flour and wheat bran's contains the same levels of T2 and HT2 toxin and we therefor combine these into the category "Wheat", and makes summary data for the exposure assessment. Ninety nine percent of the wheat flour analyses were below LOD, while 83% of the analyses of wheat bran was below LOD. For oat flakes approximately 50% of the analyses were below LOD.


Cleaning the Norwegian data from 2015 to 2023
```{r}
# Occurance_NO_2015 <- Occurance_NO_2015to23 %>% dplyr::select(c("PARAMCODE_BASE_ID", "ANMATCODE_BASE_ID", "RESVAL", "RESLOD", "RESLOQ"))
# Occurance_NO_2015 <- Occurance_NO_2015 %>% filter(str_detect(PARAMCODE_BASE_ID, c("T-2|HT-2"))) # select for the T-2 and HT-2 toxin
# 
# write.xlsx(Occurance_NO_2015,
#            file = file.path(newday, "Occurance_NO_2015.xlsx"),
#            colNames = TRUE, borders = "rows"
# )




colnames(Occurance_NO_2015) <- c("type", "FoodEx", "value", "RESLOD", "RESLOQ") # Change column names

# Make a new column called raw with the name of the food/grain in that row
Occurance_NO_2015 <- Occurance_NO_2015 %>%
  mutate(raw = case_when(
    str_detect(str_to_lower(FoodEx), "oat") ~ "oat",
    str_detect(str_to_lower(FoodEx), "wheat") ~ "wheat",
    str_detect(str_to_lower(FoodEx), "rye") ~ "rye",
    str_detect(str_to_lower(FoodEx), "cereal") ~ "cereal",
    TRUE ~ NA_character_  # eller "ukjent" hvis du vil ha en verdi
  ))

# Change the punctuation mark from comma to full stop 
Occurance_NO_2015$value <- gsub(",", ".", Occurance_NO_2015$value)
Occurance_NO_2015$RESLOD <- gsub(",", ".", Occurance_NO_2015$RESLOD)
Occurance_NO_2015$RESLOQ <- gsub(",", ".", Occurance_NO_2015$RESLOQ)

Occurance_NO_2015 <- Occurance_NO_2015 %>%  mutate(across(c(value, RESLOD, RESLOQ), as.numeric))

# Wheat
#--------------

Occurance_NO_2015_wheat <- Occurance_NO_2015 %>% filter(str_detect(FoodEx, "Wheat"))

# Merge the values from LOD and LOQ
Occurance_NO_2015_wheat <- Occurance_NO_2015_wheat %>%
  mutate(LOD_Q = if_else(is.na(RESLOD), RESLOQ, RESLOD))

# Replace the NA's with LOD or LOQ, medium bound

Occurance_NO_2015_wheat <- Occurance_NO_2015_wheat %>%
  mutate(value = case_when(
    is.na(value) & !is.na(LOD_Q) ~ LOD_Q / 2,
    TRUE ~ value
  ))


# check if cereals has any positive analyses

Occurance_NO_2015_cereal <- Occurance_NO_2015 %>% filter(str_detect(FoodEx, "Cereals"))

# Merge the values from LOD and LOQ
Occurance_NO_2015_cereal <- Occurance_NO_2015_cereal %>%
  mutate(LOD_Q = if_else(is.na(RESLOD), RESLOQ, RESLOD))

# Replace the NA's with LOD or LOQ, medium bound

Occurance_NO_2015_cereal <- Occurance_NO_2015_cereal %>%
  mutate(value = case_when(
    is.na(value) & !is.na(LOD_Q) ~ LOD_Q / 2,
    TRUE ~ value
  ))



# check for the positive analyses in oat

Occurance_NO_2015_oat <- Occurance_NO_2015 %>% filter(str_detect(FoodEx, "Oat"))

# Merge the values from LOD and LOQ
Occurance_NO_2015_oat <- Occurance_NO_2015_oat %>%
  mutate(LOD_Q = if_else(is.na(RESLOD), RESLOQ, RESLOD))

# Replace the NA's with LOD or LOQ, medium bound

Occurance_NO_2015_oat <- Occurance_NO_2015_oat %>%
  mutate(value = case_when(
    is.na(value) & !is.na(LOD_Q) ~ LOD_Q / 2,
    TRUE ~ value
  ))



```


Combine the Norwegian data from 2008-2010 and 2015-2023, and make summary data and calculate mu and var. Loc is the same as mu and var is the same as sigma

```{r}
# Combine the data for wheat flour and wheat bran  for 2008-2010

Occurance_NO_2008_wheat <- rbind(Occurance_NO_2008_wheat_flour, Occurance_NO_2008_bran)

# Combine all data for 2008-2010 and 2015-2023

Occurance_NO_wheat <- rbind(Occurance_NO_2008_wheat, Occurance_NO_2015_wheat)
Occurance_NO_oat <- rbind(Occurance_NO_2008_oat, Occurance_NO_2015_oat)
Occurance_NO_cereal <- Occurance_NO_2015_cereal


```


Separate the Occurance data for T-2 and HT-2 toxin
```{r}

#T-2
Occurance_NO_wheat_T2 <- Occurance_NO_wheat %>% filter(type == "T-2"|type == "T-2 toxin")
Occurance_NO_wheat_T2 <- Occurance_NO_wheat_T2 %>% dplyr::select(!c("FoodEx"))

conc_t2_wheat_sum <- f_summ(Occurance_NO_wheat_T2)
conc_t2_wheat_sum$Loc <- f_lognorm_Loc(conc_t2_wheat_sum)
conc_t2_wheat_sum$shape <- f_lognorm_shape(conc_t2_wheat_sum)

Occurance_NO_oat_T2 <- Occurance_NO_oat %>% filter(type == "T-2"|type == "T-2 toxin")
Occurance_NO_oat_T2 <- Occurance_NO_oat_T2 %>% dplyr::select(!c("FoodEx"))

conc_t2_oat_sum <- f_summ(Occurance_NO_oat_T2)
conc_t2_oat_sum$Loc <- f_lognorm_Loc(conc_t2_oat_sum)
conc_t2_oat_sum$shape <- f_lognorm_shape(conc_t2_oat_sum)
conc_t2_oat_sum$foodcat <- "oat"

Occurance_NO_cereal_T2 <- Occurance_NO_cereal %>% filter(type == "T-2"|type == "T-2 toxin")
Occurance_NO_cereal_T2 <- Occurance_NO_cereal_T2 %>% dplyr::select(!c("FoodEx"))

conc_t2_cereal_sum <- f_summ(Occurance_NO_cereal_T2)
conc_t2_cereal_sum$Loc <- f_lognorm_Loc(conc_t2_cereal_sum)
conc_t2_cereal_sum$shape <- f_lognorm_shape(conc_t2_cereal_sum)
conc_t2_cereal_sum$foodcat <- "cereal"

#HT-2
Occurance_NO_wheat_HT2 <- Occurance_NO_wheat %>% filter(type == "HT-2"|type == "HT-2 toxin")
Occurance_NO_wheat_HT2 <- Occurance_NO_wheat_HT2 %>% dplyr::select(!c("FoodEx"))

conc_ht2_wheat_sum <- f_summ(Occurance_NO_wheat_HT2)
conc_ht2_wheat_sum$Loc <- f_lognorm_Loc(conc_ht2_wheat_sum)
conc_ht2_wheat_sum$shape <- f_lognorm_shape(conc_ht2_wheat_sum)

Occurance_NO_oat_HT2 <- Occurance_NO_oat %>% filter(type == "HT-2"|type == "HT-2 toxin")
Occurance_NO_oat_HT2 <- Occurance_NO_oat_HT2 %>% dplyr::select(!c("FoodEx"))

conc_ht2_oat_sum <- f_summ(Occurance_NO_oat_HT2)
conc_ht2_oat_sum$Loc <- f_lognorm_Loc(conc_ht2_oat_sum)
conc_ht2_oat_sum$shape <- f_lognorm_shape(conc_ht2_oat_sum)
conc_ht2_oat_sum$foodcat <- "oat"

Occurance_NO_cereal_HT2 <- Occurance_NO_cereal %>% filter(type == "HT-2"|type == "HT-2 toxin")
Occurance_NO_cereal_HT2 <- Occurance_NO_cereal_HT2 %>% dplyr::select(!c("FoodEx"))

conc_ht2_cereal_sum <- f_summ(Occurance_NO_cereal_HT2)
conc_ht2_cereal_sum$Loc <- f_lognorm_Loc(conc_ht2_cereal_sum)
conc_ht2_cereal_sum$shape <- f_lognorm_shape(conc_ht2_cereal_sum)
conc_ht2_cereal_sum$foodcat <- "cereal"


```


# Convert occurrence in grain to concentrations in food

## "Baking" of bakery products

Taking the receipts from the Norwegian "matvaretabell" or from the Norwegian dietary calculation system "KBS". Since the EuroMix study is registered in KBS and the consumption of different food are calculated in KBS, I have selected the receipts form KBS.

We only use the information of flour/grain to calculate the T2/HT2 content in ng/g bakery products. Since the concentration of T2 is very similar in wheat and rye, all bakery products without oat is collected in the broad food category "bakery products", which includes fine bakery products such as bread (not oatbread), buns and rolls, crispbread. 
I assume that ground whole wheat contains the same concentration as wheat grain, and that this can be exchanged with oat grain to "bake" the oat bread.
The concentration of T2/HT2 in the grain will be sampled from a log normal distribution based on the summary data from a combination of all publications in the occurrence database, and the number of sampled T2/HT2 concentration in the bakry products will equal the number on analyses reported in these publications. 

The summary T2/HT2 concentration files for each food category will be merged into one data frame

### Bread and fine bakery with only wheat and rye



```{r}
# T2
bakery_t2 <- f_MC_bakery(conc_t2_wheat_sum)
bakery_t2 <- as_tibble(bakery_t2[1,1,])
conc_t2_bakery_sum <- f_summ(bakery_t2)
conc_t2_bakery_sum$Loc <- f_lognorm_Loc(conc_t2_bakery_sum)
conc_t2_bakery_sum$shape <- f_lognorm_shape(conc_t2_bakery_sum)
conc_t2_bakery_sum$foodcat <- "bakery"

# HT2
bakery_ht2 <- f_MC_bakery(conc_ht2_wheat_sum)
bakery_ht2 <- as_tibble(bakery_ht2[1,1,])
conc_ht2_bakery_sum <- f_summ(bakery_ht2)
conc_ht2_bakery_sum$Loc <- f_lognorm_Loc(conc_ht2_bakery_sum)
conc_ht2_bakery_sum$shape <- f_lognorm_shape(conc_ht2_bakery_sum)
conc_ht2_bakery_sum$foodcat <- "bakery"

```


### Oat bread

```{r}
# T2
oatbread_t2 <- f_MC_oatbread(conc_t2_wheat_sum, conc_t2_oat_sum)
oatbread_t2 <- as_tibble(oatbread_t2[1,1,])
conc_t2_oatbread_sum <- f_summ(oatbread_t2)
conc_t2_oatbread_sum$Loc <- f_lognorm_Loc(conc_t2_oatbread_sum)
conc_t2_oatbread_sum$shape <- f_lognorm_shape(conc_t2_oatbread_sum)
conc_t2_oatbread_sum$foodcat <- "oatbread"

# HT2
oatbread_ht2 <- f_MC_oatbread(conc_ht2_wheat_sum, conc_ht2_oat_sum)
oatbread_ht2 <- as_tibble(oatbread_ht2[1,1,])
conc_ht2_oatbread_sum <- f_summ(oatbread_ht2)
conc_ht2_oatbread_sum$Loc <- f_lognorm_Loc(conc_ht2_oatbread_sum)
conc_ht2_oatbread_sum$shape <- f_lognorm_shape(conc_ht2_oatbread_sum)
conc_ht2_oatbread_sum$foodcat <- "oatbread"


```



### Oatmilk

```{r}
# T2
oatmilk_t2 <- f_MC_oatmilk( conc_t2_oat_sum)
oatmilk_t2 <- as_tibble(oatmilk_t2[1,1,])
conc_t2_oatmilk_sum <- f_summ(oatmilk_t2)
conc_t2_oatmilk_sum$Loc <- f_lognorm_Loc(conc_t2_oatmilk_sum)
conc_t2_oatmilk_sum$shape <- f_lognorm_shape(conc_t2_oatmilk_sum)
conc_t2_oatmilk_sum$foodcat <- "oatmilk"

# HT2
oatmilk_ht2 <- f_MC_oatmilk(conc_ht2_oat_sum)
oatmilk_ht2 <- as_tibble(oatmilk_ht2[1,1,])
conc_ht2_oatmilk_sum <- f_summ(oatmilk_ht2)
conc_ht2_oatmilk_sum$Loc <- f_lognorm_Loc(conc_ht2_oatmilk_sum)
conc_ht2_oatmilk_sum$shape <- f_lognorm_shape(conc_ht2_oatmilk_sum)
conc_ht2_oatmilk_sum$foodcat <- "oatmilk"

```


### Merge the concentration datasets

```{r}
# T2
concentration_foodcat_t2 <- rbind(conc_t2_oat_sum, conc_t2_bakery_sum)
concentration_foodcat_t2 <- rbind(concentration_foodcat_t2, conc_t2_oatbread_sum)
concentration_foodcat_t2 <- rbind(concentration_foodcat_t2, conc_t2_cereal_sum)
concentration_foodcat_t2 <- rbind(concentration_foodcat_t2, conc_t2_oatmilk_sum)

# HT2
concentration_foodcat_ht2 <- rbind(conc_ht2_oat_sum, conc_ht2_bakery_sum)
concentration_foodcat_ht2 <- rbind(concentration_foodcat_ht2, conc_ht2_oatbread_sum)
concentration_foodcat_ht2 <- rbind(concentration_foodcat_ht2, conc_ht2_cereal_sum)
concentration_foodcat_ht2 <- rbind(concentration_foodcat_ht2, conc_ht2_oatmilk_sum)

```


# Calulate the T2/HT2 exposure

Here we will calculate the T2 and HT2 exposure from the consumption of food that can contain toxin. This will be done probabilistic by multiplying the gram eaten food from EuroMix in the food consumption file with Monte Carlo simulation of the T2/HT2 concentration in the different food categories with 1000 iterations. This will be done separately for all meals that contains T2/HT2 toxin for per individual.

```{r}
# T2
Exposure_T2 <- f_MC_Sim(Consumption, concentration_foodcat_t2)
Exposure_T2 <- Exposure_T2 %>% dplyr::select(Idkode, Day, Time, foodcat, V1:V1000)

# HT2
Exposure_HT2 <- f_MC_Sim(Consumption, concentration_foodcat_ht2)
Exposure_HT2 <- Exposure_HT2 %>% dplyr::select(Idkode, Day, Time, foodcat, V1:V1000)
```

Make a summary table for the markdown document
```{r}
# T2
Exposure_T2_sum <- Exposure_T2
Exposure_T2_sum$mean <- rowMeans(Exposure_T2_sum[,5:1004])
Exposure_T2_sum$P95 <- apply(Exposure_T2_sum[,5:1004],1, quantile, probs = 0.95, na.rm = TRUE)
Exposure_T2_sum <- Exposure_T2_sum %>% dplyr::select("Day", "Time", "foodcat", "mean", "P95")


set_flextable_defaults(font.size = 9, theme_fun = theme_vanilla)
Exposure_T2_sum %>% 
  flextable() %>% 
  colformat_double(digits = 0)

# HT2
Exposure_HT2_sum <- Exposure_HT2
Exposure_HT2_sum$mean <- rowMeans(Exposure_HT2_sum[,5:1004])
Exposure_HT2_sum$P95 <- apply(Exposure_HT2_sum[,5:1004],1, quantile, probs = 0.95, na.rm = TRUE)
Exposure_HT2_sum <- Exposure_HT2_sum %>% dplyr::select("Day", "Time", "foodcat", "mean", "P95")


set_flextable_defaults(font.size = 9, theme_fun = theme_vanilla)
Exposure_HT2_sum %>% 
  flextable() %>% 
  colformat_double(digits = 0)
```


## Save the T2 and HT2 (ng) exposure file
```{r}
write.xlsx(Exposure_T2,
           file = file.path(newday, "Exposure_T2.xlsx"),
           colNames = TRUE, borders = "rows"
)

write.xlsx(Exposure_HT2,
           file = file.path(newday, "Exposure_HT2.xlsx"),
           colNames = TRUE, borders = "rows"
)
```


# Plots

## Contribution from different food categories

```{r}

# T2
Exp_T2_plot <- Exposure_T2 %>% dplyr::select(Idkode, foodcat, V1:V1000)
Exp_T2_plot <- Exp_T2_plot %>% tidyr::pivot_longer(cols = c(contains("V")), names_to = "T2",
                                                   values_to = "value")


# HT2
Exp_HT2_plot <- Exposure_HT2 %>% dplyr::select(Idkode, foodcat, V1:V1000)
Exp_HT2_plot <- Exp_HT2_plot %>% pivot_longer(cols = c(contains("V")), names_to = "HT2",
                                                   values_to = "value")

```


```{r}

# T2
Plot_T2_meal <- ggplot(data = Exp_T2_plot, aes(y=value, x=foodcat)) +
  geom_boxplot(fill="grey")+
  theme_minimal()+
  scale_y_log10(limits=c(0.5,100000), labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 90, size = 20), axis.title = element_text(size = 24),
        axis.text.y = element_text(size = 20),legend.position= "none")+
  xlab("Food category")+
  ylab("T2 per meal (ng)")
  #annotate("text", x=9, y=40, label="Diary", size=9)

Plot_T2_meal


ggsave(filename=file.path(newday, "Plot_T2_meal.jpeg"),
       device = NULL,
       width=NA,
       height=NA,
       units="mm")

# HT2
Plot_HT2_meal <- ggplot(data = Exp_HT2_plot, aes(y=value, x=foodcat)) +
  geom_boxplot(fill="grey")+
  theme_minimal()+
  scale_y_log10(limits=c(0.5,100000), labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 90, size = 20), axis.title = element_text(size = 24),
        axis.text.y = element_text(size = 20),legend.position= "none")+
  xlab("Food category")+
  ylab("HT2 per meal (ng)")
  #annotate("text", x=9, y=40, label="Diary", size=9)

Plot_HT2_meal


ggsave(filename=file.path(newday, "Plot_HT2_meal.jpeg"),
       device = NULL,
       width=NA,
       height=NA,
       units="mm")




```

