---
title: "Exposure_T2_HT2_Euromix"
author: "Trine Husøy"
date: "2023-06-20"
output:
  word_document: default
  html_document:
    df_print: paged
---

Define knitr chunk options

For more info in Markdown and knitr chunk options see [rmarkdown-cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html)
```{r setup, include=TRUE}
knitr::opts_chunk$set(
  comment = "#>", echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, fig.width = 6)
```

# Activate packages
```{r}


library(writexl)
library(plyr)
library(openxlsx)
library(tidyverse)
library(fitdistrplus)
library(ggridges)
library(flextable)

```

# Get work directory and organise results

```{r}

HOME <- "F:/Forskningsprosjekter/PDB 1996 - EUROMIX - European t_/Forskningsfiler/TRHU/R/T2-HT2"
setwd(HOME)

```

Create a folder with current date in the Result folder
```{r}

newday <- file.path('F:/Forskningsprosjekter/PDB 1996 - EUROMIX - European t_/Forskningsfiler/TRHU/R/T2-HT2/Results', Sys.Date())
dir.create(newday)

```

# Read in data

To knit the file to word or html we need to chande the code below from "./Data/......." to "../Data/........", putting in an extra dot before the /Data.
```{r}
ID <- read_csv2("./Data/Selected_ID.csv") # The IDs in EuroMix selected for the T2/HT2 project
Consumption <- read_csv2("./Data/Food_consumption_EuroMix_meals_bothdays.csv", locale = locale(encoding = "UTF-8"))
Occurrence_R <- read_delim("./Data/Overview_occurrence_T2HT2_Rudolf_310523.csv")
```

## To be able to read æ,ø and å run in the console the code below.

 Then it will be possible to search for words with scandinavian letters
```{r}
##### IMPORTANT
Sys.setlocale(locale='no_NB.utf8')
```


# Functions

This is a function whith make R recognise scandinavian letters æ, ø and å. Makes it possible to search in the norwegian food categories
```{r}
# Create a function to convert all columns to UTF-8 encoding,
# dropping any characters that can't be converted.
f_df_convert_utf8 <- function(df_data){

  # Convert all character columns to UTF-8
  # Source: https://stackoverflow.com/questions/54633054/dbidbwritetable-invalid-multibyte-string
  df_data[,sapply(df_data,is.character)] <- sapply(
    df_data[,sapply(df_data,is.character)],
    iconv,"WINDOWS-1252","UTF-8",sub = "")
  
  return(df_data)
}

```

Calculate the location (Loc) and scale (shape) parameters for a log normal distribution
```{r}

f_lognorm_Loc <- function(x){
  log(
    x$mean^2/sqrt(x$sd^2+x$mean^2)
  )
  
}


f_lognorm_shape <- function(x){
  sqrt(
    log(
      1 + x$sd^2/x$mean^2
    )
  )
}
```

The function gives N, mean and sd for a numeric vector
```{r}
f_summ <-function(x){
  x %>%
  dplyr::summarise(
    N = n(),
    mean = mean(value, na.rm=TRUE),
    sd=sd(value, na.rm=TRUE)
  )
}  
```

This function sample the concentrations from a log normal distribution of T2 or HT2 toxin measured in grain for each publication equal to the number of analyses that has been done. The sampled concentrations for each grain is added and summary data is calculated as a basis for a overall log normal distribution of concentrations of T2 and HT2 toxin in the grain. The overall conc distribution is used for "baking" of bread, fine bakery and crisp bread.
```{r}


#-----------------------------------------------------------------------------------
# never introduce a local variable with the same name as an input variable
# just define x as list with length equal to nrow(y)
# combine all elements of list with unlist(.)
# carefully check your indexing; R is very sloppy in this respect
#-----------------------------------------------------------------------------------


f_conc_grain <- function(y){
   x <- vector("list", length = nrow(y))
  for(i in 1:nrow(y)){
    set.seed(123)
    x[[i]] <- rlnorm(n=y$sample_size[i], y$mu[i], y$var[i])
  }
  x <- unlist(x)
  x <- list(name = 1:length(x), value = x)
  x <- as_tibble(x)
  x <- f_summ(x) # make summary data
  x$Loc <- f_lognorm_Loc(x) # Location parameter for the log normal distribution
  x$shape <- f_lognorm_shape(x) # Shape parameter for the log normal distribution
  return(x)
}

```


## Functions for calculating T2/HT2 concentrations in bakery products, oat bread and cereals
Taking the receipts from the Norwegian "matvaretabell" or from the Norwegian dietary calculation system "KBS". Since the EuroMix study is registered in KBS and the consumption of different food are calculated in KBS, I have selected the receipts form KBS.

Bread with 50-70% grain contents for 100g bread:
37.3 g ground wheat 
37.3 g ground whole wheat
37.3 g water
1.3 g yeast
1 g salt

Oat bread:
38.1 g "ground" wheat 
38.1 g oat grain
38.1 g water
1.1 g yeast
1.5 g salt


```{r}
f_MC_bakery <- function(y){ # T2/HT2 (ng) concentration in g bakery
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.746 * rlnorm(n=1,y$Loc[i], y$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

f_MC_oatbread <- function(y, z){ # T2/HT2 (ng) concentration in g oatbread
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.381 * rlnorm(n=1,y$Loc[i], y$shape[i]) + 0.381 * rlnorm(n=1,z$Loc[i], z$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

```

For cereals the declaration of content shows that oat is on the top three ingredients that is listed, which means that oat is a major ingredient in cereals sold in Norway. For the cereal with fruit (AXA), oat were listed before fruit(25%), which means that the content of oat is higher than 25%. I therefore assume that the oat content is 30% in all cereals eaten in Euromix. Since the cereals also contain wheat grain and rye, I assume that 60% of the cereal is wheat and rye

```{r}
f_MC_cereal <- function(y, z){ # T2/HT2 (ng) concentration in g cereal, y is cons in oat, and z is conc in wheat_rye
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.3 * rlnorm(n=1,y$Loc[i], y$shape[i]) + 0.6 * rlnorm(n=1,z$Loc[i], z$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

```

For the oatmilk we have no defined receipt how much oat per ml water is used in commercial products, but from receipt online about 50-200 g out is used to 1000ml water. This results in 800 ml drink. This is in line with what is reported in UK with 10-12 g oat per 100 ml water. I choose to use 100 g per 1000 ml water, which results in 800 ml, which amount to approximately 10% oat. 

```{r}
f_MC_oatmilk <- function(y){ # T2/HT2 (ng) concentration in g oatmilk, y is cons in oat
  set.seed(123)
  MC <- y$N
  x <- array(dim = c(nrow(y),1,MC))
  for (u in 1:MC){
    for(i in 1:nrow(y)){
      x[i,1,u] <- (0.1 * rlnorm(n=1,y$Loc[i], y$shape[i])) # Uses T2/HT2 cons in whole grain also for ground wheat due to lack of data
  }
 }
  return(x)
}

```

## Function for doing the Monte Carlo simmulation 


```{r}
f_MC_Sim <- function(x,y){
  x$Loc <- y$Loc[match(x$foodcat, y$foodcat)] # Identify the right Loc and shape parameter for the food category
  x$shape <- y$shape[match(x$foodcat, y$foodcat)]
  
  MC <- replicate(1000, x$Amount*
                    rlnorm(n=148,x$Loc, x$shape), simplify = FALSE)
  
  df_MC <- as.data.frame(do.call(cbind, MC))
  x <- cbind(x, df_MC)
  
  return(x)
  }

```


# Cleaning of data

Separate IDs for day 1 and day 2, to be used for selection of IDs of the consumption file
```{r}
ID_day1 <- ID[ID$Day==1,]
ID_day2 <- ID[ID$Day==2,]

```


## Clean consumption data
```{r}

# Use the function f_df_convert_utf8 to be able to read Norwegian letters, æ, ø, and å
Consumption <- f_df_convert_utf8(Consumption)
Consumption <- Consumption %>% dplyr::select(-Food_nr)

Consumption_day1 <- Consumption[Consumption$Day==1,] # Separate consumption for day 1 and day 2
Consumption_day2 <- Consumption[Consumption$Day==2,]

# Select the IDs included in the T2/HT2 project

Consumption_day1 <- Consumption_day1[Consumption_day1$Idkode %in% ID_day1$IDkode,]
Consumption_day2 <- Consumption_day2[Consumption_day2$Idkode %in% ID_day2$IDkode,]

Consumption_T2 <- rbind(Consumption_day1, Consumption_day2)

```

### Select the consumption relevant for exposure to T2/HT2 toxin

This is dependent on the concentration file on T2/HT2 toxin and the food categories represented there. We will select these food categories from the consumption file, and group them into broader consumption goups.

```{r}

cereals <- c("(?i)Havrefras", "(?i)Crusli", "(?i)mysli", "(?i)frokost", "(?i)cornflakes", "(?i)4-korn") # I decided to not include "frø" (seeds)
cereal <- Consumption_T2[str_detect(Consumption_T2$Name, paste(cereals, collapse = "|")),]
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, paste(cereals, collapse = "|")),]
cereal$foodcat <- "cereal"

oat <- Consumption_T2[str_detect(Consumption_T2$Name, "(?i)havregryn"),]
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, "(?i)havregryn"),]
oat$foodcat <- "oat"
Consumption <- rbind(cereal, oat)

oat <- Consumption_T2[str_detect(Consumption_T2$Name, "(?i)havr"),] # Extract food with oat
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, "(?i)havr"),]
oatbread <- oat[str_detect(oat$Name, "(?i)brød"),] # Extract the bread with oat
oatbread$foodcat <- "oatbread"
Consumption <- rbind(Consumption, oatbread)
oat <- oat[!str_detect(oat$Name, "(?i)brød"),]

oatmilk <- oat[str_detect(oat$Name, "(?i)melk"),]
oatmilk$foodcat <- "oatmilk"
Consumption <- rbind(Consumption, oatmilk)

bakery_fine <- c("(?i)rundst", "(?i)boll", "(?i)tortilla", "(?i)hamburgerbrød", "(?i)polarbrød", "(?i)brød", "(?i)knekkebr", "(?i)rug sammalt", "(?i)hvete")
bakery <- Consumption_T2[str_detect(Consumption_T2$Name, paste(bakery_fine, collapse = "|")),]
Consumption_T2 <- Consumption_T2[!str_detect(Consumption_T2$Name, paste(bakery_fine, collapse = "|")),]
bakery$foodcat <- "bakery"
Consumption <- rbind(Consumption, bakery)

Consumption <- Consumption %>% arrange(Idkode, Meal) # arrange the file after ID and meals
Consumption$Amount <- as.numeric(Consumption$Amount)
```


## Clean Occurrence data

The concentration of T2 and HT2 in grain's need to be sorted according to level of T2 and HT2, and the summary data are converted to individual concentration data by sampling from a log normal distribution defined by the summary data in each paper. The number of individual data sampled is equal to the number of analyses provided by the paper. 
It was decided to merge the concentration data on wheat and rye, because they are in the same range and they gave the same concentration of T2 toxin after calculation of T2 in bakery products. 
This leave us with two concentration distributions, one for wheat and rye combined ("wheat_rye") and one for oat ("oat"). This is based on the samples individual concentration from each paper, from here the location parameter (Loc = mu) and shape parameter (shape=sigma) are calculated. These define the new long normal distribution for all concentration data. 

```{r}
# T2 conc in grain
conc_t2_raw <- Occurrence_R[Occurrence_R$type == "T-2",] # Select the rows with T2 conc
conc_t2_raw <- conc_t2_raw[!is.na(conc_t2_raw$raw),] # Delete the rows with NAs
conc_t2_raw <- conc_t2_raw %>% dplyr::select("type", "raw", "sample_size", "mu", "var", "ref")

conc_t2_oat <- conc_t2_raw[conc_t2_raw$raw == "Oats",]
conc_t2_wheat <- conc_t2_raw[conc_t2_raw$raw == "Wheat",]
conc_t2_rye <- conc_t2_raw[conc_t2_raw$raw == "Rye",]
conc_t2_wheat_rye <- rbind(conc_t2_wheat, conc_t2_rye)

# HT2 conc in grain
conc_ht2_raw <- Occurrence_R[Occurrence_R$type == "HT-2",] # Select the rows with HT2 conc
conc_ht2_raw <- conc_ht2_raw[!is.na(conc_ht2_raw$raw),] # Delete the rows with NAs
conc_ht2_raw <- conc_ht2_raw %>% dplyr::select("type", "raw", "sample_size", "mu", "var", "ref")

conc_ht2_oat <- conc_ht2_raw[conc_ht2_raw$raw == "Oats",]
conc_ht2_wheat <- conc_ht2_raw[conc_ht2_raw$raw == "Wheat",]
conc_ht2_rye <- conc_ht2_raw[conc_ht2_raw$raw == "Rye",]
conc_ht2_wheat_rye <- rbind(conc_ht2_wheat, conc_ht2_rye)

```


### Make one concentration distribution and summary data for each grain type

```{r}
# T2 
conc_t2_wheatrye_sum <- f_conc_grain(conc_t2_wheat)
conc_t2_oat_sum <- f_conc_grain(conc_t2_oat)
conc_t2_oat_sum$foodcat <- "oat"

# HT2
conc_ht2_wheatrye_sum <- f_conc_grain(conc_ht2_wheat)
conc_ht2_oat_sum <- f_conc_grain(conc_ht2_oat)
conc_ht2_oat_sum$foodcat <- "oat"
```


# Convert occurrence in grain to concentrations in food

## "Baking" of bakery products

Taking the receipts from the Norwegian "matvaretabell" or from the Norwegian dietary calculation system "KBS". Since the EuroMix study is registered in KBS and the consumption of different food are calculated in KBS, I have selected the receipts form KBS.

We only use the information of flour/grain to calculate the T2/HT2 content in ng/g bakery products. Since the concentration of T2 is very similar in wheat and rye, all bakery products without oat is collected in the broad food category "bakery products", which includes fine bakery products such as bread (not oatbread), buns and rolls, crispbread. 
I assume that ground whole wheat contains the same concentration as wheat grain, and that this can be exchanged with oat grain to "bake" the oat bread.
The concentration of T2/HT2 in the grain will be sampled from a log normal distribution based on the summary data from a combination of all publications in the occurrence database, and the number of sampled T2/HT2 concentration in the bkary products will equal the number on analyses reported in these publications. 

The summary T2/HT2 concentration files for each food category will be merged into one data frame

### Bread and fine bakery with only wheat and rye



```{r}
# T2
bakery_t2 <- f_MC_bakery(conc_t2_wheatrye_sum)
bakery_t2 <- as_tibble(bakery_t2[1,1,])
conc_t2_bakery_sum <- f_summ(bakery_t2)
conc_t2_bakery_sum$Loc <- f_lognorm_Loc(conc_t2_bakery_sum)
conc_t2_bakery_sum$shape <- f_lognorm_shape(conc_t2_bakery_sum)
conc_t2_bakery_sum$foodcat <- "bakery"

# HT2
bakery_ht2 <- f_MC_bakery(conc_ht2_wheatrye_sum)
bakery_ht2 <- as_tibble(bakery_ht2[1,1,])
conc_ht2_bakery_sum <- f_summ(bakery_ht2)
conc_ht2_bakery_sum$Loc <- f_lognorm_Loc(conc_ht2_bakery_sum)
conc_ht2_bakery_sum$shape <- f_lognorm_shape(conc_ht2_bakery_sum)
conc_ht2_bakery_sum$foodcat <- "bakery"

```


### Oat bread

```{r}
# T2
oatbread_t2 <- f_MC_oatbread(conc_t2_wheatrye_sum, conc_t2_oat_sum)
oatbread_t2 <- as_tibble(oatbread_t2[1,1,])
conc_t2_oatbread_sum <- f_summ(oatbread_t2)
conc_t2_oatbread_sum$Loc <- f_lognorm_Loc(conc_t2_oatbread_sum)
conc_t2_oatbread_sum$shape <- f_lognorm_shape(conc_t2_oatbread_sum)
conc_t2_oatbread_sum$foodcat <- "oatbread"

# HT2
oatbread_ht2 <- f_MC_oatbread(conc_ht2_wheatrye_sum, conc_ht2_oat_sum)
oatbread_ht2 <- as_tibble(oatbread_ht2[1,1,])
conc_ht2_oatbread_sum <- f_summ(oatbread_ht2)
conc_ht2_oatbread_sum$Loc <- f_lognorm_Loc(conc_ht2_oatbread_sum)
conc_ht2_oatbread_sum$shape <- f_lognorm_shape(conc_ht2_oatbread_sum)
conc_ht2_oatbread_sum$foodcat <- "oatbread"


```

### Cereals

```{r}
# T2
cereal_t2 <- f_MC_cereal(conc_t2_oat_sum, conc_t2_wheatrye_sum)
cereal_t2 <- as_tibble(cereal_t2[1,1,])
conc_t2_cereal_sum <- f_summ(cereal_t2)
conc_t2_cereal_sum$Loc <- f_lognorm_Loc(conc_t2_cereal_sum)
conc_t2_cereal_sum$shape <- f_lognorm_shape(conc_t2_cereal_sum)
conc_t2_cereal_sum$foodcat <- "cereal"

# HT2
cereal_ht2 <- f_MC_cereal(conc_ht2_oat_sum, conc_ht2_wheatrye_sum)
cereal_ht2 <- as_tibble(cereal_ht2[1,1,])
conc_ht2_cereal_sum <- f_summ(cereal_ht2)
conc_ht2_cereal_sum$Loc <- f_lognorm_Loc(conc_ht2_cereal_sum)
conc_ht2_cereal_sum$shape <- f_lognorm_shape(conc_ht2_cereal_sum)
conc_ht2_cereal_sum$foodcat <- "cereal"



```

### Oatmilk

```{r}
# T2
oatmilk_t2 <- f_MC_oatmilk( conc_t2_oat_sum)
oatmilk_t2 <- as_tibble(oatmilk_t2[1,1,])
conc_t2_oatmilk_sum <- f_summ(oatmilk_t2)
conc_t2_oatmilk_sum$Loc <- f_lognorm_Loc(conc_t2_oatmilk_sum)
conc_t2_oatmilk_sum$shape <- f_lognorm_shape(conc_t2_oatmilk_sum)
conc_t2_oatmilk_sum$foodcat <- "oatmilk"

# HT2
oatmilk_ht2 <- f_MC_oatmilk(conc_ht2_oat_sum)
oatmilk_ht2 <- as_tibble(oatmilk_ht2[1,1,])
conc_ht2_oatmilk_sum <- f_summ(oatmilk_ht2)
conc_ht2_oatmilk_sum$Loc <- f_lognorm_Loc(conc_ht2_oatmilk_sum)
conc_ht2_oatmilk_sum$shape <- f_lognorm_shape(conc_ht2_oatmilk_sum)
conc_ht2_oatmilk_sum$foodcat <- "oatmilk"

```


### Merge the concentration datasets

```{r}
# T2
concentration_foodcat_t2 <- rbind(conc_t2_oat_sum, conc_t2_bakery_sum)
concentration_foodcat_t2 <- rbind(concentration_foodcat_t2, conc_t2_oatbread_sum)
concentration_foodcat_t2 <- rbind(concentration_foodcat_t2, conc_t2_cereal_sum)
concentration_foodcat_t2 <- rbind(concentration_foodcat_t2, conc_t2_oatmilk_sum)

# HT2
concentration_foodcat_ht2 <- rbind(conc_ht2_oat_sum, conc_ht2_bakery_sum)
concentration_foodcat_ht2 <- rbind(concentration_foodcat_ht2, conc_ht2_oatbread_sum)
concentration_foodcat_ht2 <- rbind(concentration_foodcat_ht2, conc_ht2_cereal_sum)
concentration_foodcat_ht2 <- rbind(concentration_foodcat_ht2, conc_ht2_oatmilk_sum)

```


# Calulate the T2/HT2 exposure

Here we will calculate the T2 and HT2 exposure from the consumption of food that can contain toxin. This will be done probabilistic by multiplying the gram eaten food from EuroMix in the food consumption file with Monte Carlo simulation of the T2/HT2 concentration in the different food categories with 1000 iterations. This will be done separately for all meals that contains T2/HT2 toxin for per individual.

```{r}
# T2
Exposure_T2 <- f_MC_Sim(Consumption, concentration_foodcat_t2)
Exposure_T2 <- Exposure_T2 %>% dplyr::select(Idkode, Day, Time, foodcat, V1:V1000)

# HT2
Exposure_HT2 <- f_MC_Sim(Consumption, concentration_foodcat_ht2)
Exposure_HT2 <- Exposure_HT2 %>% dplyr::select(Idkode, Day, Time, foodcat, V1:V1000)
```

Make a summary table for the markdown document
```{r}
# T2
Exposure_T2_sum <- Exposure_T2
Exposure_T2_sum$mean <- rowMeans(Exposure_T2_sum[,5:1004])
Exposure_T2_sum$P95 <- apply(Exposure_T2_sum[,5:1004],1, quantile, probs = 0.95)
Exposure_T2_sum <- Exposure_T2_sum %>% dplyr::select("Day", "Time", "foodcat", "mean", "P95")


set_flextable_defaults(font.size = 9, theme_fun = theme_vanilla)
Exposure_T2_sum %>% 
  flextable() %>% 
  colformat_double(digits = 0)

# HT2
Exposure_HT2_sum <- Exposure_HT2
Exposure_HT2_sum$mean <- rowMeans(Exposure_HT2_sum[,5:1004])
Exposure_HT2_sum$P95 <- apply(Exposure_HT2_sum[,5:1004],1, quantile, probs = 0.95)
Exposure_HT2_sum <- Exposure_HT2_sum %>% dplyr::select("Day", "Time", "foodcat", "mean", "P95")


set_flextable_defaults(font.size = 9, theme_fun = theme_vanilla)
Exposure_HT2_sum %>% 
  flextable() %>% 
  colformat_double(digits = 0)
```


## Save the T2 and HT2 (ng) exposure file
```{r}
write.xlsx(Exposure_T2,
           file = file.path(newday, "Exposure_T2.xlsx"),
           colNames = TRUE, borders = "rows"
)

write.xlsx(Exposure_HT2,
           file = file.path(newday, "Exposure_HT2.xlsx"),
           colNames = TRUE, borders = "rows"
)
```


# Plots

## Contribution from different food categories

```{r}
# T2
Exp_T2_plot <- Exposure_T2 %>% dplyr::select(Idkode, foodcat, V1:V1000)
Exp_T2_plot <- Exp_T2_plot %>% pivot_longer(cols = c(contains("V")), "T2")

# HT2
Exp_HT2_plot <- Exposure_HT2 %>% dplyr::select(Idkode, foodcat, V1:V1000)
Exp_HT2_plot <- Exp_HT2_plot %>% pivot_longer(cols = c(contains("V")), "HT2")
```


```{r}

# T2
Plot_T2_meal <- ggplot(data = Exp_T2_plot, aes(y=value, x=foodcat)) +
  geom_boxplot(fill="grey")+
  theme_minimal()+
  scale_y_log10(limits=c(0.5,100000), labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 90, size = 20), axis.title = element_text(size = 24),
        axis.text.y = element_text(size = 20),legend.position= "none")+
  xlab("Food category")+
  ylab("T2 per meal (ng)")
  #annotate("text", x=9, y=40, label="Diary", size=9)

Plot_T2_meal


ggsave(filename=file.path(newday, "Plot_T2_meal.jpeg"),
       device = NULL,
       width=NA,
       height=NA,
       units="mm")

# HT2
Plot_HT2_meal <- ggplot(data = Exp_HT2_plot, aes(y=value, x=foodcat)) +
  geom_boxplot(fill="grey")+
  theme_minimal()+
  scale_y_log10(limits=c(0.5,100000), labels = scales::comma)+
  theme(axis.text.x = element_text(angle = 90, size = 20), axis.title = element_text(size = 24),
        axis.text.y = element_text(size = 20),legend.position= "none")+
  xlab("Food category")+
  ylab("HT2 per meal (ng)")
  #annotate("text", x=9, y=40, label="Diary", size=9)

Plot_HT2_meal


ggsave(filename=file.path(newday, "Plot_HT2_meal.jpeg"),
       device = NULL,
       width=NA,
       height=NA,
       units="mm")




```


# Make summary data for the manuscript

```{r}
Exposure_T2_HT2 <- Exposure_T2
Exposure_T2_HT2[,5:1004] <- Exposure_T2[,5:1004] + Exposure_HT2[,5:1004]

Exposure_T2_HT2$per1 <- ifelse(Exposure_T2_HT2$Time<1200, 1, Exposure_T2_HT2$Time)
Exposure_T2_HT2$per2 <- ifelse(1200<=Exposure_T2_HT2$per1 & Exposure_T2_HT2$per1<1800, 2, Exposure_T2_HT2$per1)
Exposure_T2_HT2$periode <- ifelse(1800 <= Exposure_T2_HT2$per2, 3, Exposure_T2_HT2$per2)

Exposure_total <- Exposure_T2_HT2[,5:1004]
Exposure_total$periode <- Exposure_T2_HT2$periode
#Exposure_total$IDkode <- Exposure_T2_HT2$Idkode

Exposure_total <- Exposure_total %>%  pivot_longer(!periode, names_to = "MC", values_to = "value")

Sum_1 <-function(x){
  x %>%
    group_by(periode) %>%
    summarise(
      N = n(),
      mean = mean(value, na.rm=TRUE),
      sd=sd(value, na.rm=TRUE),
      min=min(value, na.rm=TRUE),
      P05=quantile(value, .05, na.rm=TRUE),
      P50=quantile(value, .50, na.rm=TRUE),
      P95=quantile(value, .95, na.rm=TRUE),
      max=max(value, na.rm=TRUE)
    )
} 

Sum_2 <-function(x){
  x %>%
    group_by(periode) %>%
    exp(mean(log(value)))
} 


Exposure_sum <- Sum_1(Exposure_total)

Exposure_sum

Exposure_total <- as.data.frame(Exposure_total)

Condition1 <- Exposure_total$periode == 1
Condition2 <- Exposure_total$periode == 2
Condition3 <- Exposure_total$periode == 3

Periode1 <- Exposure_total$value[Condition1]
Periode2 <- Exposure_total$value[Condition2]
Periode3 <- Exposure_total$value[Condition3]                                

GM1 <- exp(mean(log(Periode1))) 
GM2 <- exp(mean(log(Periode2)))
GM3 <- exp(mean(log(Periode3)))
     
GM3


```





